\subsection{Roles and responsibilities}
The following key roles have been defined for this project:

\begin{small}	

	\begin{longtable}{>{\raggedright\arraybackslash}p{2.5cm} >{\raggedright\arraybackslash}p{2.8cm} >{\raggedright\arraybackslash}p{2.6cm}>{\raggedright\arraybackslash}p{5.2cm}}
	
		\toprule[2pt]

		\textbf{Role} & \textbf{Resource Name} & \textbf{Organization} & \textbf{Responsibilities} 
		\\ \midrule[1.5pt] 
		\endhead

		Project Sponsor & Luís Manuel Pérez Llera & European Commission & Supervise the project. \\ \midrule

		Project Manager & Pol Fontanes Molina & HIRO & Manage the project. \\ \midrule

		Project Secretary & Sílvia González García & HIRO & Administrate the internal documents and information of the group. \\ \midrule

		Financial Manager & Santiago Lopezbarrena Arenas & HIRO & Estimate and control the costs of the project. \\ \midrule

		Stakeholders \& Procurement Manager & Eva María Urbano González & HIRO & Identify the stakeholders of the project and manage and control their engagement.\newline 
		Plan, conduct and control the procurements of the project.\\ \midrule
		
		Scope \& Time Manager & Marina Pons Daza & HIRO & Define and control the scope and deadlines of the project. \\ \midrule

		Risk Manager & Borja Calderón Rosario & HIRO & Identify and manage the possible risks of the project. \\ \midrule

		Quality Manager & Guillermo Escartín Vivancos & HIRO & Control that the quality requirements of the project are met. \\ \midrule

		Technical Managers & David Pérez Sánchez, \newline  Hamza Nachett, \newline  Laura Pla Olea & HIRO & Analyse and control the technical aspects of the project. \\ \midrule

		Marketing \& Communications Managers & Albert Herrando Moraira, \newline  María De Benedicto Barba & HIRO & Promote the project and its final product.\newline Search for possible customers.\newline 
		Ensure communication between the different members of the group. \\ \midrule

		Research \& Development assessor & Matthew Perren & Airbus Defence and Space GmbH & Collaboration in the research and production of satellite sensors. \\ \midrule

		Legal \& Business Assessor & Oliver Heinrich & BHO Legal Rechtsanwälte Partnership & Business and legal advice. \\ \midrule

		Research \& Development Assessor & Ismael López & Deimos Space S.L.U. & Design and development of satellite sensors and systems. \\ \midrule

		Application collaborator & Jean-François Rapp & ICUBE-SERTIT & Advice in the application of data provided by EO satellites. \\ \midrule

		Application collaborator & Vessela Samoungi & Remote Sensing Application Center (ReSAC) & Advice in the application of remote sensing and geographic information systems (GIS) to be used for land cover, land use and urban planning. \\ \midrule

		Development \& Testing collaborator & Philippe Keryer & Thales Alenia Space SAS & Design, development, integration and testing of space systems. \\ \midrule

		Development \& Application collaborator & Steven Krekels & VITO nv & Advice in the use of remote sensing for land use. Development of new remote sensing systems, sensors and platforms. 
		\\ \bottomrule[2pt]

		\caption{Roles and responsibilities}
		\label{table_roles}	
	\end{longtable}
	\end{small}
