\section{Participants roles and responsabilities}
As previously stated, this section will provide the reader with the roles and responsibilities of the different DEOS-UD staff in terms of the Communication Plan. In this section, different committees and teams will also be described. 

\textbf{Steering Committee}
\newline
\newline
The steering committee will provide DEOS-UD with solutions to problems along with strategic command in order to ensure a correct and efficient development of the project. As this team’s role is of extreme importance when it comes to the project’s success, a careful selection of its representatives must be performed. The steering committee will be composed of the members with key roles in DEOS-UD project; these members are listed in the following table, extracted from the first project charter. 

[TABLA]



As described, the team will not only work as a steering committee but also as an advisory committee, for this reason it will be composed by multiple consortium members that will act as advisors in diverse fields. 
The key roles developed by the steering committee are detailed below. 
 \begin{itemize}
 	\item	Take and implement management decisions that affect a significant part of the stakeholders. 
 	\item	Take action in important schedule delays as well as cost overruns by modifying resources assigned to departments, staff planning, or anything necessary to redirect situations that endanger a correct development of the project.
 	\item 	Offer leadership, guidance and support to problems that smaller groups have not been able to solve by themselves. 
 	\item Enhance communication skills along with communications procedures in order to avoid communication-related problems.
 \end{itemize}

\textbf{Project Manager}
\newline
\newline
DEOS-UD Project manager, Pol Fontanes Molina, is the person in charge of assuring that every aspect of the project is functioning as planned. He is ought to detect, communicate and correct any deviations (schedule variances, cost overruns and scope changes) from the original plans. The decisions taken by the PM, will be communicated directly to the steering committee, members of which will communicate to the rest of the staff.

\textbf{Advisory committee}
\newline
\newline
Participants in the advisory committee are detailed here.
 \begin{itemize}
 	\item  Research and Development assessors: 
 	\begin{itemize}
 		\item Matthew Perren (Airbus Defence and Space GmbH)
 		\item Ismael López (Deimos Space)
 	\end{itemize}
 \item 	Legal and Business Assessor
 \begin{itemize}
 	\item Oliver Heinrich (BHO Legal)
  \end{itemize}
\item Application collaborators
\begin{itemize}
	\item Jean François Rapp (ICUBE-SERTIT)
	\item Vessela Samoungi (ReSAC)
\end{itemize}
\item Development and Application collaborator
 \begin{itemize}
	\item Steven Krekels (VITO nv)
\end{itemize}
 \end{itemize}

The function of this committee will be that of providing tailored assistance in anything related with the project in order to solve issues and avoid risks during DEOS-UD development. Given the importance of this group itself, its participants will meet with the steering group regularly to ensure a correct use and implementation of their know-hoy inside DEOS-UD. 

\textbf{Business Project Team}
\newline
\newline
This team will be directed by Santiago Lopezbarrena Arenas, the financial manager, and is in charge of assuring an economical resources correct management by providing careful tracing in the use of the budget along with a proper staff training in means of economical performance. This team is also ought to communicate the project manager with the latest information on earned value management parameters in order for the latter to know at what point exactly the development of the project is found.   
 
\textbf{Technical Project Team}
\newline
\newline
The Technical Project Team, conducted by its three leaders David Pérez Sánchez, Hamza Nachett and Laura Pla Olea, will be in charge of analysing and controlling every single technical aspect of the project. The team itself must assure that everything done during DEOS-UD project development meets the requirements of the contract by successfully following all de documentation and activities received from the overall project staff, including contractors and subcontractors as well. As part of its essential activities, the Technical Project Team is expected to resolve and to give advice in any inconveniences or issues that may appear during the course of the project. 
The Technical Project Team’s leaders will be part of the Steering group and will report regularly to the project manager on topics that concern the technical progresses of DEOS-UD project, by having gathered all the information related to this subject from the different departments developing such activities. 

\textbf{Oversight }
\newline
\newline
For the sake of a reliable accomplishment of the project’s goals along with a recognized meeting of the contract’s specifications, an oversight agency will actively work with DEOS-UD mostly when different milestones are achieved and a certification in the results is needed. The company auditing DEOS-UD results will be Bureau Veritas and its specific responsibilities are detailed here.
 \begin{itemize}
	\item 	Auditing a correct implementation of the different requirements of the contract regarding privacy policies with data management. 
	\item 	Auditing a correct implementation of the different requirements of the contract regarding privacy policies with data management. 
	\item 	Auditing a correct implementation of the different requirements of the contract regarding privacy policies with data management. 
\end{itemize}
Given that an auditory is an external agency, it has not been included the advisory team; yet its collaboration inside the project is key to a successful accomplishment of the project’s goals. 
