\subsection{Scope}


The SCOPE for this project is:

{\bfseries Engineering} 
\begin{itemize}

	\item Research and analysis of the current space applications and requirements of the following optical and radar systems:

		\begin{itemize}

		\item LIDAR
		\item Radar
		\item Super-spectral
		\item Hyperspectral
		\item Limb sounders
		\item Gravimetry
		\item High quantum efficiency photodectectos
		\item High precisition optical beam scanning and pointing
		\item Advanced infrared technologies

		\end{itemize}

	\item Research of the contributions of current space technologies to urban development.

	\item Selection of the most promising systems to profit Earth Observation to air composition and terrain analysis.
	
	\item Development of sensor's preliminary design defining the minimum performance parameters in order to improve the existing technologies.

	\item ¿¿¿Interaction platform ???

	\item Development of a mock-up by following the preliminary design.

	\item Testing and validation of the prototype in a space simulated environment.

	\item Design closure and development of the product.

\end{itemize}

{\bfseries Business planning and exploitation of results}
\begin{itemize}
	\item Market analysis and of the potential suppliers and selection of these.
	\item Market analysis of the potential costumers.
	\item Elaboration of a business plan. 

\end{itemize}

\textbf{Quality} \textit{esto no acaba de parecer apropiado en el scope}
\begin{itemize}
	\item Every document goes through four stages to be approved:
	\begin{itemize}
		\item{-} Guidelines preparation
		\item{-} Document revision
		\item{-} Document rectification
		\item{-} Document approval
	\end{itemize}
	\item Elaboration of periodic reports in order to have continuous control over the development of the project.

\end{itemize}

\textbf{Communication and dissemination strategies} \textit{esto no acaba de parecer apropiado en el scope}

\begin{itemize}
	\item Implementation of a dissemination plan to announce the product combining online and offline dissemination.	
	 \item Development of 
	  a website. 
	  \item Use of social media marketing power. 
	  \item Conduct several conferences.
	  \item  Let to know the product improvements through technology demonstrators.
\end{itemize}




