\section{Work plan — Work packages, deliverables}

Brief description of the section

\subsection{Overall Structure}

Brief presentation of the overall structure of the work plan. \textbf{Network diagram SOLO de los WP o diagrama explicativo del proyecto. El network diagram que tenemos ahora está en D2 Apartado 3.2.}

\subsection{Timing of the Work Plan}

Timing of the different WP: \textbf{Gantt chart. D2 Apartado 6}

\subsection{Description of Work Packages}

\begin{itemize}

\item List of WP. \textbf{D2 Apartado 2.1 Poner solo WP, no todas las activities. Extraer del D2 también Start Month i End Month}

\item Description of each WP. \textbf{Extraer información de D2 sección 2 (Número de participantes, líder, objetivos, etc.) Hay que poner las diferentes tareas dentro de cada WP y quienes participan en cada tarea. Importante: Falta calcular PM por participante. Deliverables asociados a cada WP ( también a extraer del D2).}

\end{itemize}

\begin{longtable}[H]{p{1.3cm} p{2cm} p{1.8cm} p{2cm} p{1.9cm} p{1.6cm} p{1.4cm}}
	\toprule[2pt]
	
	\textbf{Work Package No.} & \textbf{Work Package Title} & \textbf{Lead Participant No.} & \textbf{Lead Participant Short Name} & \textbf{Person Months} & \textbf{Start Month} & \textbf{End Month} \\
	
	\midrule[1.5pt] 
	\endhead
	
	 &  &  &  &  &  & \vspace{0.2cm} \\
	
	\midrule

	 &  &  &  &  &  & \vspace{0.2cm} \\
	
	\midrule
	
	 &  &  &  &  &  &  \vspace{0.2cm} \\

	\midrule

 	 &  &  &  &  &  &  \vspace{0.2cm} \\
	
	\bottomrule[2pt]
	
	\caption{List of work packages}
	\label{workpackages}
\end{longtable}


\subsection{Deliverables}

List of deliverables and milstones. \textbf{D2 sección 1.2}

KEY: Deliverable numbers in order of delivery dates. Please use the numbering convention <WP number>.<number of deliverable within that WP>.

For example, deliverable 4.2 would be the second deliverable from work package 4.

Type: Use one of the following codes:
\begin{itemize}
\item R: Document, report (excluding the periodic and final reports) 
\item DEM: Demonstrator, pilot, prototype, plan designs
\item DEC: Websites, patents filing, press i media actions, videos, etc. 
\item OTHER: Software, technical diagram, etc.
\end{itemize}

Dissemination level: Use one of the following codes:
\begin{itemize}
\item PU = Public, fully open, e.g. web
\item CO = Confidential, restricted under conditions set out in Model Grant Agreement
\item CI = Classified, information as referred to in Commission Decision 2001/844/EC.
\end{itemize}

Deliverable Date: Measured in months from the project start date (month 1)

\begin{longtable}[H]{p{1.8cm} p{2cm} p{1.3cm} p{1.8cm} p{1.3cm} p{2.1cm} p{1.8cm}}
	\toprule[2pt]
	
	\textbf{Deliverable No.} & \textbf{Deliverable Name} & \textbf{Work Package No.} & \textbf{Lead Participant Short Name} & \textbf{Type} & \textbf{Disemination Level} & \textbf{Deliverable Date} \\
	
	\midrule[1.5pt] 
	\endhead
	
	&  &  &  &  &  & \vspace{0.2cm} \\
	
	\midrule

	 &  &  &  &  &  & \vspace{0.2cm} \\
	
	\midrule
	
	 &  &  &  &  &  &  \vspace{0.2cm} \\

	\midrule

 	 &  &  &  &  &  &  \vspace{0.2cm} \\
	
	\bottomrule[2pt]
	
	\caption{List of Deliverables}
	\label{workpackages}
\end{longtable}


\subsection{Inter-relation between components}

Graphical presentation of the components showing how they inter-relate (Per chart or similar) \textbf{Algo más sencillo que el network diagram. Podría ser el network diagram.}


