\section{Management structure, milestones and procedures}

\subsection{Organisational Structure}

A complex organizational structure has been established given the complexity and scale of the project. On top of the organizational chain, a steering committee has been created and it will provide DEOS-UD with strategic command and solutions to problems that affect a significant part of the stakeholders in order to ensure a correct and efficient development of the project. Hand-to-hand with the steering committee, the advisory committee will provide the project leaders with tailored assistance in order to assure time and cost-efficient decisions are taken. There is also a business project team which will be in charge of assuring an economical resources correct management by providing careful tracing in the use of the budget along with a proper staff training in means of economic performance; the team is also ought to keep the steering committee updated with the latest information on earned value management parameters so that appropriate decisions are taken. Reinforcing the organizational structure of the project, a technical project team has been created as well in order to provide control over technical decisions in the project.
An organizational structure directed by a steering committee is specifically designed to fit such a large-scale and long-term project as this one is. The experience, capacities and diversity of the members it is composed by will play a key role in the outcome of the project while maintaining an efficient use of time and resources. The steering committee will take major decisions involving a significant fraction of the stakeholders. The business project team will be in charge of assessing the decisions involving budget modification or inter-department budget redistribution. Finally, decisions involving a modification or significant change in the technologies used during DEOS-UD progress will be in hands of the technical project team. Smaller affairs along with local inconveniences will be solved by the specific group affected by them. By having such a decision making distribution, DEOS-UD ensures a correct importance of the decision to experience ratio and thus assuring a more efficient time usage by providing every person within DEOS-UD with fitted responsibilities.
The milestones to accomplish are detailed in the following section; extracted from the third deliverable.      

\subsection{Acceptance Criteria and Milestones}

\textbf{Milestones: D2 apartado 1.3. Acceptance Criteria: D2 apartado 1.4 Poner toda la tabla.}

Based on the previous deliverables, the following criteria when stating a specific work package is established:
\begin{itemize} 	
	\item \textbf{WP1}: Management 
	\item \textbf{WP2}: Quality and administration
	\item \textbf{WP3}: State of the art
	\item \textbf{WP4}: Product development
	\item \textbf{WP5}: Simulation, testing and validation
	\item \textbf{WP6}: Business planning
	\item \textbf{WP7}: Communication and dissemination
	\item \textbf{WPx}: All Work Packages
\end{itemize}

The following table summarizes the milestones, including the work packages to which they are related, their due date and means of verification.

\begin{longtable}[H]{p{1.5cm} p{2.8cm} p{2.2cm} p{2cm} p{3.2cm} }
	\toprule[2pt]
	
	\textbf{Milestone No.} & \textbf{Milestone Name} & \textbf{Related WP} & \textbf{Due Date} & \textbf{Means of Verification} \\
	
	\midrule[1.5pt] 
	\endhead
	
	1 & Kick off meeting & WPx & 10/09/2018 & Agenda and Meeting Minutes \vspace{0.2cm} \\
	
	\midrule

	2 & Project management plan & WP1 & 05/10/2018 & Archived soft copy and management team evaluation meeting \vspace{0.2cm} \\
	
	\midrule
	
	3 & Business plan & WP6 & 05/10/2018 & Archived soft copy and business team evaluation meeting \vspace{0.2cm} \\

	\midrule

 	4 & Communication plan & WP7 & 05/10/2018 & Archived soft copy and marketing and communication team evaluation meeting \vspace{0.2cm} \\
 	 
 	\midrule
 	 
 	5 & State of the art completion & WP3 & 28/12/2018 & Archived soft copy and management and technical team evaluation meeting \vspace{0.2cm} \\
 	
 	\midrule
 
 	6 & Payload preliminary design & WP4 & 14/06/2019 & Technical documents review and technical team evaluation meeting \vspace{0.2cm} \\
 
 	\midrule
 
  	7 & Modular system preliminary design & WP4 & 06/09/2019 & Technical documents review and technical team evaluation meeting \vspace{0.2cm} \\
 
 	\midrule
 
 	8 & Interaction platform preliminary design & WP4 & 29/11/2019 & Technical documents review and technical team evaluation meeting \vspace{0.2cm} \\
 
 	\midrule
 
 	9 & Payload final design & WP4, WP2 & 12/06/2020 & Technical documents review and technical team evaluation meeting \vspace{0.2cm} \\
 
 	\midrule
 
 	10 & Modular system final design & WP4, WP2 & 04/09/2020 & Technical documents review and technical team evaluation meeting \vspace{0.2cm} \\
	
	\midrule

	11 & Interaction platform final design & WP4, WP2 & 27/11/2020 & Technical documents review and technical team evaluation meeting \vspace{0.2cm} \\

	\midrule

	12 & Prototype manufacturing & WP4 & 16/04/2021 & Prototype testing \vspace{0.2cm} \\

	\midrule

	13 & Individual systems testing & WP5 & 09/07/2021 & Systems testing \vspace{0.2cm} \\
	 
	\midrule

	14 & Full system testing & WP5 & 29/10/2021 & Full system testing \vspace{0.2cm} \\

	\midrule

	15 & Project completion & WPx & 21/01/2022 & Evaluation of all technical and non-technical documentation as well as prototype testing reports \vspace{0.2cm} \\

	\bottomrule[2pt]
	
	\caption{List of milestones}
	\label{workpackages}
\end{longtable}

\subsection{Quality Management}

The Quality management Plan defines the quality levels that must be achieved in order to accept the final product developed and the methods to ensure these levels. In this section the quality management plan is defined together with methods and tools to assure, control and improve it.
\input{./subsections/3.2.Quality_management_plan/3.2.1.Quality_assurance_approach}
\input{./subsections/3.2Quality_management_plan/3.2.2.Quality_Control_Approach}
\input{./subsections/3.2.Quality_management_plan/3.2.3.Quality_Improvement_approach}
\input{./subsections/3.2.Quality_management_plan/3.2.4.Quality_Roles_and_Responsibilities}

\subsection{Risk Management Plan}

The present section will identify the risks threatening a project's correct development, the Work Packages that will be involved in such risks and will suggest a mitigation solution for each and everyone of them. The described information is found in the following table. The previously defined Work Packages apply for this section too.

\begin{longtable}[H]{p{4cm} p{4.7cm} p{5cm}}
	\toprule[2pt]
	
	\textbf{Description of risk} & \textbf{Work package(s) involved} & \textbf{Proposed risk-mitigation measure} \\
	
	\midrule[1.5pt] 
	\endhead
	
	Deliverable delays & WPx & Dedicate more resources than expected. \vspace{0.2cm} \\
	
	\midrule

	Inaccurate cost forecast & WP1, WP2 & Consider new funding sources and revise the financial management plan. \vspace{0.2cm} \\
	
	\midrule
	
	Lack of communication & WPx & Periodical meeting and use of collaborative software.  \vspace{0.2cm} \\

	\midrule

 	Lack of technology improvement & WP4 & Guarantee the development with thorough search of state of the art technologies.  \vspace{0.2cm} \\
 	
 	\midrule
 	
 	Lack of access to project needed information & WPx & Previous accurate research is needed before the development of the project. \vspace{0.2cm} \\
 
 	\midrule

	Low team motivation & WPx & Personnel control and team building projects. \vspace{0.2cm} \\
 	
 	\midrule

	Unsuccessful quality control & WPx & Improve or increase quality controls. \vspace{0.2cm} \\
 	
 	\midrule

	Conflicts between members  & WPx & Personnel conflict resolution meetings. \vspace{0.2cm} \\
 	
 	\midrule

 	Infeasible design & WP4 & Periodical reviews with experts and managers. \vspace{0.2cm} \\
 	
 	\midrule

	Techonolgical components with security vulnerabilities & WP3, WP4, WP5 & Check for possible security problems during development through specialised companies. \vspace{0.2cm} \\
 	
 	\midrule

	Organization issues & WPx & Demand for external companies specialised advice in project management. \vspace{0.2cm} \\
 	
 	\midrule

	Stakeholder desertion & WPx (Except WP7) & Transfer responsibilities to other stakeholders when possible or contract new ones. \vspace{0.2cm} \\
 	
 	\midrule

	Competitors appearance & WP6, WP7 & Improvement of the quality-to-price ratio of the service. \vspace{0.2cm} \\
 	
 	\midrule

	Delay in external deliverables & WPx & Control the delivery schedules and change provider if necessary. \vspace{0.2cm} \\
 	
 	\midrule

	Economical market issues & WPx & Control cost evolution due to external changes throughout the project. \vspace{0.2cm} \\
 	
 	\midrule

	Components or raw material quality & WP4, WP5 & Have exhaustive and regular quality controls to avoid problems in components in the final test. \vspace{0.2cm} \\
	
	\bottomrule[2pt]
	
	\caption{Critical risks for implementation}
	\label{workpackages}
\end{longtable}

\subsection{Communication Management}

Communication management has been effectively synthesized in a table where each and every type of communication process inside DEOS-UD is concisely described. This section will set an expanded overview regarding communication during the project, and will be helpful for all departments seeking for standardized guidance when trying to communicate results, problems or suggestions to other departments or to the general public. 

\begin{landscape}
	
	
	\begin{longtable}{| >{\raggedright\arraybackslash}p{2.8cm}  | >{\raggedright\arraybackslash}p{2.8cm} | >{\raggedright\arraybackslash}p{2cm} | >{\raggedright\arraybackslash}p{2cm} | >{\raggedright\arraybackslash}p{2cm} | >{\raggedright\arraybackslash}p{2.4cm} | >{\raggedright\arraybackslash}p{2.4cm} | >{\raggedright\arraybackslash}p{2.4cm} |  }
		
		
		\toprule [2pt]
		
		\textbf{Communication Type} & \textbf{Objective of Communication} & \textbf{Medium}  &\textbf{Frequency} &\textbf{Audience}& \textbf{Owner}& \textbf{Deliverable} &\textbf{Format} \\  
		
		\midrule [1.5pt]
		\endhead
		
		Internal Business Status Meetings& Discuss assignments, activities and sharing information  & Face to Face   &  Weekly &Business Team     & Financial Manager  & Agenda, Meeting Minutes  &Soft copy archived on SharePoint site and project website\\  
		
		\hline
		
		Technical and Business Status Meetings and Reports&Discuss assignments, activities, sharing information and reporting the project status   &Face to Face    & Weekly  & Project Manager, Business Team, Technical Team, Project Secretary    &Project Manager   & Agenda, Meeting Minutes, Status Reports  &Soft copy archived on SharePoint site and project website\\  
		
		\hline
		
		Advisory Committee Meetings& Review progress, risks and issues  & Face to Face   &Monthly   &  Advisory Committee, Project Stakeholders, Project Manager, Project Secretary   &Project Manager   & Agenda, Meeting Minutes  &Soft copy archived on SharePoint site and project website\\  
		
		\hline
		
		Steering Committee Status Meetings& Enhance communication and coordination of the project  & Face to Face   & Monthly  & Steering Committee, Project Manager, Project Secretary    &  Project Manager & Agenda, Meeting Minutes  &Soft copy archived on SharePoint site and project website\\  
		
		\hline
		
		Status Meetings and Reports to Stakeholders&Report the status of the project including activities, progress, costs and issues   &Face to Face or Video Conference    &Monthly   & Stakeholders, Project Manager, Project Secretary    & Project Manager  &Agenda, Meeting Minutes, Status Reports   &Soft copy archived on SharePoint site and project website\\  
		
		\hline
		
		Project Status Reports&Provide Stakeholders information on the status and progress of the project   &Email    & Monthly  &  Project Stakeholders, Stakeholder and Procurement Manager, Project Manager   & Stakeholder and Procurement Manager  &  Project status, schedule, budget and cost tracking, status of issues and risks, health status, status of action items, future or planned activities &Soft copy archived on SharePoint site and project website\\    
		
		\bottomrule[2pt]
		
		
		\caption{Communication management plan matrix}
	\end{longtable}
	
	\vspace*{\fill}
	
	
\end{landscape}