\section{Activity list}

\begin{longtable}[H]{l >{\raggedright\arraybackslash}p{4cm} p{8cm}}
	
	\toprule[2pt]
	
	\textbf{WBS-ID} &  \textbf{Activity}  & \textbf{Description of Work} \\
	
	\midrule [1.5pt]
	\endhead
	
	1. & Project Management & All activities related with the management of the project fall under this activity.\vspace{0.2cm} \\
	
	\midrule
	
	1.1. & Development of the project management plan &Elaboration of all the documentation that states the strategy of the management and organization of the project through its duration.\vspace{0.2cm} \\
	
	\midrule
	
	1.2. & Monitoring of the project & Control of the progress of each activity of the project.\vspace{0.2cm} \\
	
	\midrule
	
	1.2.1. & Meetings & Gathering of the members of the project to inform each other of the progress.\vspace{0.2cm} \\
	
	\midrule
	
	1.2.2. & Task tracking and scheduling & Tracking of the active tasks and scheduling.\vspace{0.2cm} \\
	
	\midrule
	
	1.3. & Annual reporting & Every year that the project lasts will call for the elaboration of an internal report with the aim of keeping up to date with the progress done.\vspace{0.2cm} \\
	
	\midrule
	
	1.4. & Project implementation of risk management & Study of all the potential risks and how will they be managed so that their affectation to the project stays to a minimum.\vspace{0.2cm} \\
	
	\midrule
	
	2. & Quality and Administration & Activities related to the administrative aspects of the project and to assure the quality of all the documents presented.\vspace{0.2cm} \\
	
	\midrule
	
	2.1. & Human resources & Administration of all the employees needed to fulfil the different tasks of the project.\vspace{0.2cm} \\
	
	\midrule
	
	2.1.1. & Employment of the necessary staff & Definition of the number of employees necessary.\vspace{0.2cm} \\
	
	\midrule
	
	2.1.2. & Human resources management & Administration of all the employees needed to fulfill the different tasks of the project.\vspace{0.2cm} \\
	
	\midrule
	
	2.2. & Financial plan & Lay down of all the planned costs of the project, the funding expected from the various sources, a study on the economic feasibility of the project and a plan for additional funding search.\vspace{0.2cm} \\
	
	\midrule
	
	2.2.1. & Costs & Lay down of all the planned costs of the project.\vspace{0.2cm} \\
	
	\midrule
	
	2.2.1.1. & Fix costs & Lay down of all the fix costs of the project.\vspace{0.2cm} \\
	
	\midrule
	
	2.2.1.2. & Variable costs & Lay down of all the variable costs of the project.\vspace{0.2cm} \\
	
	\midrule
	
	2.2.2. & Funding & Lay down of all the expected funding of the project.\vspace{0.2cm} \\
	
	\midrule
	
	2.2.3. & Economic feasibility & Study on the economic feasibility of the project.\vspace{0.2cm} \\
	
	\midrule
	
	2.2.4. & Evolution monitoring & Monitoring of the evolution of the project finances.\vspace{0.2cm} \\
	
	\midrule
	
	2.2.5. & Additional and follow-up funding seek & Search for the additional funding for the project.\vspace{0.2cm} \\
	
	\midrule
	
	2.3. & Documentation management & The quality of the documents that have to be delivered through all the duration of the project is guaranteed in this activity by establishing guidelines for the redaction of all the documents, their revision and posterior rectification and final approval.\vspace{0.2cm} \\
	
	\midrule
	
	2.3.1. & Guidelines preparation & Establishment of the guidelines for the relation of all documents.\vspace{0.2cm} \\
	
	\midrule
	
	2.3.2. & Documented revision & Revision of all the documents of the project.\vspace{0.2cm} \\
	
	\midrule
	
	2.3.3. & Doctument rectification & Rectification of the documents that do not meet the project requirements.\vspace{0.2cm} \\
	
	\midrule
	
	2.3.4. & Document approval & Approval of the reviewed and rectified documents.\vspace{0.2cm} \\
	
	\midrule
	
	2.4. & Periodic monitoring & To ensure the quality of the project, a periodic monitoring of all the activities will be carried out.\vspace{0.2cm} \\
	
	\midrule
	
	3. & State of the Art & Before starting the design and research it is key to have an accurate vision of the actual state of the technology that is going to be developed.\vspace{0.2cm} \\
	
	\midrule
	
	3.1. & Payloads & For each of the sensors that are planned to be improved there is a search of the current space applications, that help defining the requirements for these sensors.\vspace{0.2cm} \\
	
	\midrule
	
	3.1.1. & Search for current space applications & Search for the current space applications.\vspace{0.2cm} \\
	
	\midrule
	
	3.1.2 & Requirements definition & Definition of the requirements for the the sensors.\vspace{0.2cm} \\
	
	\midrule
	
	3.2. & Modular system & For the modular system where each sensor will be mounted on there will be a search of current similar systems in space applications and the definition of the requirements for the one developed in this project.\vspace{0.2cm} \\
	
	\midrule
	
	3.2.1. & Search for the current modular systems with space applications & Search for the current modular systems with space applications.\vspace{0.2cm} \\
	
	\midrule
	
	3.2.2. & Requirements definition & Definition of the requirements for modular system developed in this project.\vspace{0.2cm} \\
	
	\midrule
	
	3.3. & Urban development applications & The search for current applications similar to those that want to be implemented with this project has to be carried out, in the weather forecast area, the urban planning area and the greenhouse emissions reduction area, thus defining the requirements for the applications.\vspace{0.2cm} \\
	
	\midrule
	
	3.3.1.1. & Weather forecast & Search for current applications similiar to those that want to be implemented with this project in the weather forecast area.\vspace{0.2cm} \\
	
	\midrule
	
	3.3.1.2. & Urban planning (3D models) & Search for the current applications to those that want to be implemented with this project in the urban planning area.\vspace{0.2cm} \\
	
	\midrule
	
	3.3.1.3. & Greenhouse emissions reduction (pollution) & Search for the current applications to those that want to be implemented with this project in the greenhouse emissions reduction area.\vspace{0.2cm} \\
	
	\midrule
	
	3.3.2. & Requirements definition & Definition of the requirements fotr the applications.\vspace{0.2cm} \\
	
	\midrule
	
	4. & Product development & All the phases of the development of the product are included in this activity, from the research up to the final technical specifications.\vspace{0.2cm} \\
	
	\midrule
	
	4.1. & Preliminary design & This first phase of the development is meant to include all the research and definition of the initial parameters of the different components.\vspace{0.2cm} \\
	
	\midrule
	
	4.1.1. & Payloads' preliminary design & The research and initial development of each sensor that is intended to improve is carried out in this phase.\vspace{0.2cm} \\
	
	\midrule
	
	4.1.1.1. & Research & Research for the payloads preliminary design.\vspace{0.2cm} \\
	
	\midrule
	
	4.1.1.2. & Development & Development of the payloads preliminary design.\vspace{0.2cm} \\
	
	\midrule
	
	4.1.2. & Modular system's preliminary design & Includes the initial development of the physical framework for sensor blocks, of the systems' interaction and applications, of the sensors' data fusion software and the definition of the satellite communications applications domains.\vspace{0.2cm} \\
	
	\midrule
	
	4.1.2.1. & Development of physical framework for sensor block & Modular system preliminary design and development of physiscal framework for sensor block.\vspace{0.2cm} \\
	
	\midrule
	
	4.1.2.2. & Development of systems interaction and applications & Modular system preliminary design and development of systems interactions and applications.\vspace{0.2cm} \\
	
	\midrule
	
	4.1.2.3. & Development of sensors data fusion software & Modular system preliminary design and development of sensor data fusion software.\vspace{0.2cm} \\
	
	\midrule
	
	4.1.2.4. & Definition of SATCOM applications domains & Modular system preliminary design and definition of SATCOM application domains.\vspace{0.2cm} \\
	
	\midrule
	
	4.1.3. & Interaction platform's preliminary design & Implementation of the web-based servers for sharing sensor's data, of the processing algorithms based on applications and the pre-design of a full services stakeholders platform.\vspace{0.2cm} \\
	
	\midrule
	
	4.1.3.1. & Implement web-bases servers for sharing sensors data & Preliminary design of the interaction platform. Implement web-based servers for sharing sensors data.\vspace{0.2cm} \\
	
	\midrule
	
	4.1.3.2. & Implement processing algorithms based on applications & Preliminary design of the interaction platform. Implement processing algorithms based on applications.\vspace{0.2cm} \\
	
	\midrule
	
	4.1.3.3. & Pre-design a full services stakeholders platform & Pre-design of interaction platform.\vspace{0.2cm} \\
	
	\midrule
	
	4.2. & Final design & This final phase of the product's development will define the final technical specifications of each part of the product.\vspace{0.2cm} \\
	
	\midrule
	
	4.2.1. & Payloads' final design & The design of each sensor is complete and its final technical specifications are defined.\vspace{0.2cm} \\
	
	\midrule
	
	4.2.1.1. & Sensor final design & Final design of the payload sensor.\vspace{0.2cm} \\
	
	\midrule
	
	4.2.1.2. & Sensor final technical specifications & Final decision of the technical specifications of the payload sensor.\vspace{0.2cm} \\
	
	\midrule
	
	4.2.2. & Modular system & The design of the modular system and the sensors' data fusion software is complete and their final technical specifications are defined.\vspace{0.2cm} \\
	
	\midrule
	
	4.2.2.1. & Modular system's final design & Final design of the modular system.\vspace{0.2cm} \\
	
	\midrule
	
	4.2.2.2. & Sensor data fusion software final design  & Final design of the modular system, specifically of the sensor data fusion software.\vspace{0.2cm} \\
	
	\midrule
	
	4.2.2.3. & Modular system final technical specifications & Final decision of technical specifications of the modular system.\vspace{0.2cm} \\
	
	\midrule
	
	4.2.3. & Interaction platform's final design & The design of the interaction platform is complete, including the web based servers for data sharing, the processing algorithms based on applications and the full services stakeholders platform, and their final technical specifications are defined.\vspace{0.2cm} \\
	
	\midrule
	
	4.2.3.1. & Web based servers for data sharing final implementation & Final design and implementations of the interaction platform, specifically the web servers for data sharing.\vspace{0.2cm} \\
	
	\midrule
	
	4.2.3.2. & Processing algorithms based on applications final design & Final design and implementation of the interaction platfomr, specifically the processing algorithms.\vspace{0.2cm} \\
	
	\midrule
	
	4.2.3.3. & Full service stakeholders platform implementation & Final design and implementation of the itneraction platform.\vspace{0.2cm} \\
	
	\midrule
	
	4.2.3.4. & Final technical specifications & Decision of the final technical specifications of the interaction (stakeholders) platform.\vspace{0.2cm} \\
	
	\midrule
	
	5. & Simulation, testing, validation and quality & Activities regarding the simulation, testing, validation and quality control of the final product are included in this task.\vspace{0.2cm} \\
	
	\midrule
	
	5.1. & Technology demonstrator prototype manufacturing & Manufacturing of the prototype of the product, including all its subsystems (payload sensors, modular system and interaction platform), in order to be tested in the following activities.\vspace{0.2cm} \\
	
	\midrule
	
	5.1.1. & Manufacturing of payload sensors. & Manufacturing of the sensors of the prototype, in order to be tested in the following activities.\vspace{0.2cm} \\
	
	\midrule
	
	5.1.2. & Manufacturing of modeular system. & Manufacturing of the module of the prototype, in order to be tested in the following activities.\vspace{0.2cm} \\
	
	\midrule
	
	5.1.3. & Implementation of interaction platform. & Manufacturing of the interaction platform of the prototype, in order to be tested in the following activities.\vspace{0.2cm} \\
	
	\midrule
	
	5.2 & Payload validation & Validation of the performance of the sensors mounted on the system.\vspace{0.2cm} \\
	
	\midrule
	
	5.3 & Modular system validation & Validation of the modular system performance, of the systems interaction, of the sensors' data fusion software, of the satellite communications applications domains and also of the physical framework for sensor blocks.\vspace{0.2cm} \\
	
	\midrule
	
	5.4 & Interaction platform validation & Validation of the interaction platform to check if it develops all its functions properly.\vspace{0.2cm} \\
	
	\midrule
	
	5.5 & Full system prototype validation & Validation of the whole system using the prototype in order to test its performance.\vspace{0.2cm} \\
	
	\midrule
	
	5.6 & Quality of the product & Quality control of all the subsystems of the product and all the methodologies applied on its manufacturing and validation.\vspace{0.2cm} \\
	
	\midrule
	
	6 & Business planning and exploitation of results & The activities regarding the final explotation and business planning of the product are included in this task.\vspace{0.2cm} \\
	
	\midrule
	
	6.1 & Market approach & Study of stakeholders, procurement conditions negotiation and purchase of the resourses in order to study the feasibility of the project.\vspace{0.2cm} \\
	
	\midrule
	
	6.1.1. & Study of stakeholders & Study of the possible companies interested on the project.\vspace{0.2cm} \\
	
	\midrule
	
	6.1.2. & Procurement conditions negotiation & Negotitation of the conditions of the procurement of the resources.\vspace{0.2cm} \\
	
	\midrule
	
	6.1.3. & Resources purchase & Purchase of the resources required in the project.\vspace{0.2cm} \\
	
	\midrule
	
	6.2. & Exploitation and business plans & Includes the business plan of the product to exploit its economic potential.\vspace{0.2cm} \\
	
	\midrule
	
	7. & Communication and dissemination strategies & Includes all the activities regarding the dissemination of the product inside the market.\vspace{0.2cm} \\
	
	\midrule
	
	7.1. & Dissemination and communication plan & Definition of the strategies planned to the dissemination of the final product.\vspace{0.2cm} \\
	
	\midrule
	
	7.2. & On-line dissemination activities & Include activities as the creation of a web site and the social media management.\vspace{0.2cm} \\
	
	\midrule
	
	7.2.1. & Web site development & Development of the web site to promote the product.\vspace{0.2cm} \\
	
	\midrule
	
	7.2.2. & Social media management & Management of the social media used in the dissemination plan of the project.\vspace{0.2cm} \\
	
	\midrule
	
	7.3. & Off-line dissemination activities & Participation in conferences and meetings about the field of the technology.\vspace{0.2cm} \\
	
	\midrule
	
	7.3.1. & Conferences & Attendance to conferences in order to disseminate to possible stakeholders the product.\vspace{0.2cm} \\
	
	\midrule
	
	7.3.2. & Meeting & Meeting to promote the product inside the market.\vspace{0.2cm} \\
	
	\midrule
	
	7.4. & Dissemination materials & Production of all the materials that will help to the dissemination of the product, as technology demonstrators or audio visual productions.\vspace{0.2cm} \\
	
	\midrule
	
	7.4.1. & Technology demonstrators & Production of technology demonstrators needed to the dissemination of the product.\vspace{0.2cm} \\
	
	\midrule
	
	7.4.2. & Audio visual material production & Production of all the visual material needed to the promotion of the product.\vspace{0.2cm} \\
	
	\bottomrule[2pt]
	
	\caption{Activity list and description}
\end{longtable}