\section{Project Objectives}

%\begin{center}
	\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm} >{\raggedright\arraybackslash}p{6.1cm} >{\raggedleft\arraybackslash}c}
		\toprule[2pt]
		\textbf{Project Objectives} & \textbf{Success Criteria} & \textbf{Approval Responsible} 
		\\ \midrule [1.5pt]
		\endhead
		
		\textbf{Scope} &  &  
		\\ \midrule

		Introduction and demonstration of new technologies, systems and sub-systems for EO & The systems must prove their proper functioning in a relevant environment and be able to provide the user the required data. & Project Manager \vspace{0.2cm}
		\\ \midrule
		
		\textbf{Time} &  &   
		\\ \midrule

		4 months & After the analysis of project deliverables and project milestones, a period of 44 months seems acceptable. Nevertheless, possible delays may appear during the project development. Hence, proper time-management is necessary to complete the project within the aimed duration. & Project Manager  \vspace{0.2cm}
		\\ \midrule

		\textbf{Cost} &  &   
		\\ \midrule

		4 million \euro & The estimated cost of the project is 4M  and it is detailed in the next section. Every expense of the project must be controlled and limited to avoid exceeding the budget. & Financial Manager  \vspace{0.2cm}
		\\ \midrule

		\textbf{Quality} &  &  
		\\ \midrule

		Organised, planned and detailed development with continuous improvement & 
 		Elaboration of periodic reports in order to have continuous control over the development of the project. \newline
 		Documentation must be complete, understandable and structured. & Quality Manager  \vspace{0.2cm}
 		\\	\bottomrule[2pt]

		\caption{Project Objectives}

	\end{longtable}
%\end{center}

