\section{Quality Roles and Responsibilities}
In the following table, the quality roles for this project will be stated and its responsibilities defined. These roles are important so they will be the ones to control the implementation of the quality assurance, control, and improvement.

\begin{longtable}[H]{>{\raggedright\arraybackslash}p{5cm} p{9cm}}
	
	\toprule[2pt]
	
	\textbf{Role} &  \textbf{Responsibilities}\\
	
	\midrule [1.5pt]
	\endhead
	
	Project Manager & Final responsible for the quality of the project.\vspace{0.3cm}\newline Schedules meetings with the Quality Department in order to discuss the quality aspects of the project.\vspace{0.3cm}\newline Approves the quality plans of the project.\vspace{0.2cm} \\
	
	\midrule
		
	Project Manager Secretary & Helps the Project Manager in the tasks that he/she delegates.\vspace{0.2cm} \\
	
	\midrule
	
	Quality Manager & Main quality responsible of the project.\vspace{0.3cm}\newline Fixes the quality standards that all documents are required to fulfil.\vspace{0.3cm}\newline Reviews all the deliverables to make sure they fulfil the required quality. The same documents are also reviewed by the Quality Manager Assessor.\vspace{0.2cm} \\

	\midrule
	
	Quality Manager Assessor & Helps the Quality Manager in the tasks that he/she delegates.\vspace{0.3cm}\newline Reviews all the deliverables to make sure they fulfil the required quality. The same documents are also reviewed by the Quality Manager.\vspace{0.2cm} \\
	
	\midrule
	
	Technical Manager & Coordinates the work done by the engineers and technicians.\vspace{0.3cm}\newline Defines the technical quality plan and the software quality plan.\vspace{0.3cm}\newline Performs periodic quality controls on the design of the product.\vspace{0.3cm}\newline Reviews the technical aspects of the deliverables before approving them.\vspace{0.3cm}\newline Monitors the quality control procedures of both the prototype and the final product.\vspace{0.3cm}\newline Monitors the quality control procedures of the interaction platform.\vspace{0.2cm} \\
	
	\midrule
	
	Engineers and technicians & Make sure that the design of the product follows the technical quality plan.\vspace{0.3cm}\newline Perform quality control procedures over the prototype and over the final product.\vspace{0.3cm}\newline Make sure that the design of the interaction platform follows the software quality plan.\vspace{0.3cm}\newline Validate that the interaction platform fulfils the quality standards.\vspace{0.2cm} \\
	
	\bottomrule[2pt]
	
	\caption{List of quality roles and responsibilities}
	
\end{longtable}