\section{Make or Buy decisions}
In this section, the WBS work packages that will be outsourced are identified. The reasons to buy these work packages, the estimated cost, risk and other important parameters to take into account are shown in Table \ref{procurementtable}.


\begin{landscape}
	
	\begin{longtable}[H]{ >{\raggedright\arraybackslash}p{1cm}  >{\raggedright\arraybackslash}p{2.7cm}  >{\raggedright\arraybackslash}p{3.5cm}  >{\raggedright\arraybackslash}p{1.7cm}  >{\raggedright\arraybackslash}p{2cm}  >{\raggedright\arraybackslash}p{2.5cm}  >{\raggedright\arraybackslash}p{2.5cm}  >{\raggedright\arraybackslash}p{4cm}  }
		
		\toprule[2pt]
		
		\textbf{WBS ID} &  \textbf{Work Package Name}  & \textbf{Reasons for BUY} & \textbf{Cost estimate} & \textbf{Type of contract} & \textbf{Possible risks} & \textbf{List of suppliers} & \textbf{Special considerations or constraints} \\
		
		\midrule[1.5pt]
		
		
		
		5.1.1. & Manufacturing of payload sensors & Create sensors with the designed parameters, using high performance industry standards.  & 125.900 \euro & FFP (Firm Fixed Price contract) & Delay in delivering the products.\newline Faulty products.  & Neptec Technologies \newline Satellite Imaging Corporation& Products must satisfy design parameters. \newline Maximum due date 16/04/21  \\
		
		\hline
		
		5.1.2. & Manufacturing of modular system & Use sensor interface specific outsource facilities for manufacturing the modular system   & 123.086 \euro & FFP (Firm Fixed Price contract) & Delay in delivery.\newline Specifications not met. & Curtis-Wright Solutions & Product must satisfy design parameters. \newline Maximum due date 16/04/21 \\
		
		\hline
		
		5.6. & Quality of the product & An entity external to the project must do the quality tests. & 93.248 \euro & FFP (Firm Fixed Price contract) & Quality standards of the products not met.& ESA & Due date of quality study is fixed on 21/01/22\\
		
		\hline
		
		7.2.1.& Web site development & Quick launch of the project professional website. & 17.957 \euro & FFP (Firm Fixed Price contract) & Late delivery. \newline Not meeting communication plan specifications & Intechnic \newline Llungelizard \newline & Due date before 21/01/22\\
		
		\hline
		
		 & Auditing  & External company for auditing and supervising & 160.000\euro & FFP (Firm Fixed Price Contract) & Wrongly audit the work done.  & Bureau Veritas & Deliveries during the whole project.\\
		
			
		
		
		\bottomrule[2pt]
		\caption{List of procurement items}
		\label{procurementtable}
	\end{longtable}

\end{landscape}

