\section{Statement Of Work}
For each procurement option 

Detailed description of the procurement item;
• Requirements to be met by the procurement item;
• Type of contract to be used;
• Setting the scheduled dates in each contract for the contract deliverables (milestones) and coordinating with the schedule project development;
• Any constraints and assumptions that could affect planned procurements;
• Identifying requirements for performance bonds or insurance contracts to mitigate some forms of project risk;
• Establishing the form and format to be used for the procurement/contract statements of work;
• Identifying prequalified sellers, if any, to be used; and
• Procurement metrics to be used to manage contracts and evaluate sellers.

5.1.1. Manufacturing of payload sensors
\begin{itemize}
	\item[\textbf{Requirements}] Build sensors described by the 4.2.1.0. Payloads final design, related to the Earth Observation project. Seller can manufacture one part of the required items, but budget will be adjusted accordingly.  
	\item[\textbf{Type of contract}] A Firm Fixed Price contract is stipulated because, for this tasks there are clear requirements and determined deadlines. Also, budget have been assigned and a final product version it is clearly decided.
	\item[\textbf{Scheduled date}] To be delivered no later than 16/04/2021. Starts after the 4.2.1.0.Payloads final design delivery and is part of the 5.0. Prototype manufacturing milestone.
	\item[\textbf{Constraints}] Manufactured sensors should met all 4.2.1.0. Payloads final design constraints without exception.
	\item[\textbf{Risk control actions}] description
	\item[\textbf{Form and format}] description
	\item[\textbf{Prequalified sellers}] description
	\item[\textbf{Procurement metrics}] description
\end{itemize}