\section{Definitions of impacts by objective}

To evaluate the impact into the overall project if a certain risk did happen, a numerical estimate it is provided to quantify the effects of the risks in terms of Scope and Quality, Schedule and Cost. Those three categories are scaled from 1 to 5 in a linear way in order to quantify the impact, where 1 is the minimum and 5 is the maximum. Moreover, each effect is defined qualitatively depending on its category and its impact. 

\begin{longtable}[H]{l >{\raggedright\arraybackslash}p{6.3cm} p{3.5cm}}
	
	\toprule[2pt]
	
	\textbf{Scope/Quality Impact} &  \textbf{Description}  & \textbf{Scope Impact Score} \\
	
	\midrule [1.5pt]
	\endhead
	
	Very High & Be unable to achieve the desired objectives. The project end item is effectively useless. & 5 
	\vspace{0.2cm} \\
	
	\midrule
	
	High & Scope and quality reduction hardly acceptable. The impact makes that the project item quality is below the desired objectives and under the acceptance criteria. & 4 
	\vspace{0.2cm} \\
	
	\midrule
	
	Medium & The risk produces moderate impact in the project and the results. Major areas of the scope are affected and quality is reduced but still above the acceptance criteria. & 3
	\vspace{0.2cm} \\

	\midrule

	Low & It produces a low impact. Minor areas of the scope are affected and quality is lightly reduced affecting very demanding applications. & 2
	\vspace{0.2cm} \\

	\midrule

	Very Low & It produces and insignificant impact in the project. Scope and quality decrease barely noticeable. & 1
	\vspace{0.2cm} \\
		
	\bottomrule[2pt]
	
	\caption{Scope/Quality impacts}

\end{longtable}




\begin{longtable}[H]{l >{\raggedright\arraybackslash}p{6.6cm} p{4cm}}
	
	\toprule[2pt]
	
	\textbf{Schedule Impact} &  \textbf{Description}  & \textbf{Schedule Impact Score} \\
	
	\midrule [1.5pt]
	\endhead
	
	Very High & Very significant delay in the schedule, increasing the milestone duration more than a 20\%.  & 5
	\vspace{0.2cm} \\
	
	\midrule
	
	High & Significant delay in the schedule, increasing the milestone duration between a 10\% and 20\%. & 4
	\vspace{0.2cm} \\
	
	\midrule
	
	Medium & Moderate delay in the schedule, increasing the milestone duration between a 5\% and 10\%. & 3
	\vspace{0.2cm} \\

	\midrule

	Low & Slightly significant delay in the schedule, increasing the milestone duration less than 5\%. & 2
	\vspace{0.2cm} \\

	\midrule

	Very Low & Insignificant delay and time increase. & 1
	\vspace{0.2cm} \\
		
	\bottomrule[2pt]
	
	\caption{Schedule imapcts}

\end{longtable}




\begin{longtable}[H]{l >{\raggedright\arraybackslash}p{7.8cm} p{3.5cm}}
	
	\toprule[2pt]
	
	\textbf{Cost Impact} &  \textbf{Description}  & \textbf{Cost Impact Score} \\
	
	\midrule [1.5pt]
	\endhead
	
	Very High & Several impact on the project cost, increasing the cost about more than 30\%. & 5
	\vspace{0.2cm} \\
	
	\midrule
	
	High & Important impact on the project cost, increasing the cost about 15\% to 30\%. & 4
	\vspace{0.2cm} \\
	
	\midrule
	
	Medium & Moderate impact on the project cost, increasing the cost about 10\% to 15\%. & 3
	\vspace{0.2cm} \\

	\midrule

	Low & Reduced impact on the project cost, increasing the cost about  less than 10%. & 2
	\vspace{0.2cm} \\

	\midrule

	Very Low & Insignificant impact on the project cost. & 1
	\vspace{0.2cm} \\
		
	\bottomrule[2pt]
	
	\caption{Cost impacts}

\end{longtable}