\section{Project Deliverables}

All the deliverables specified in the Table \ref{PDel} will be submitted to the European Commission during the development of the project. 

\begin{longtable}[H]{p{4cm}p{10cm}}
	
	\toprule[2pt]
	
	\textbf{Deliverable Name} & \textbf{Description} \\ 
	
	\midrule[1.5pt] 
	\endhead
	
	
	Project Management Plan & 
	Document with detailed explanation of the project management strategies, including the Project Charter, stakeholder register, risk, quality and financial plans. 
	\vspace{0.2cm}
	\\ \midrule
	
	Communication Plan  & 
	Document containing all the planned dissemination strategies, such as the online communication (including website development and social media management), the offline communication (participation in meetings and conferences) and the dissemination materials (technology demonstrators). 
	\vspace{0.2cm}
	\\ \midrule

	Payload State of the Art  & 
	Report containing the state of the art of current EO remote sensors as well as the sensors to improve selection and the first requirements definition.  
	\vspace{0.2cm}
	\\ \midrule

	Modular System State of the Art  & 
	Report containing the state of the art of current modular systems with space applications and its first requirements definition.  
	\vspace{0.2cm}
	\\ \midrule

	Space Applications State of the Art & 
	Report containing the state of the art of current urban development space applications and first interaction platforms requirement definition.  
	\vspace{0.2cm}
	\\ \midrule

	Payload Preliminary Design  & 
	Report determining the payload preliminary design. It contains the research, requirements and preliminary performances parameters of each sensor.
	 \vspace{0.2cm}
	\\ \midrule

	Modular System Preliminary Design  & 
	Report detailing the modular system preliminary design. It includes a first review of the sensors blocks physical framework and sensors data fusion software requirements as well as the initial definition of the SATCOM application domains. 
	\vspace{0.2cm}
	\\ \midrule

	Interaction Platform Preliminary Design  & 
	Report detailing the interaction platform preliminary design. It includes the predesign of data sharing servers and platforms as well as the definition of the initial implementation of data processing algorithms.  
	\vspace{0.2cm}
	\\ \midrule
	
	Mid-term Review & 
	Document used to check the current state of the project, in order to inform all the participants, including the stakeholders, of the progress. 
	\vspace{0.2cm}
	\\ \midrule
	
	Payload Final Design  & 
	Report detailing the final design and technical specifications of each developed sensor. 
	\vspace{0.2cm}
	\\ \midrule

	Modular System  Final Design  & 
	Report detailing the final design and technical specifications of the modular system. 
	\vspace{0.2cm}
	\\ \midrule

	Sensors Data Fusion Software  & 
	Final sensors data fusion software.
	\vspace{0.2cm}
	\\ \midrule

	Interaction Platform Final Design  & 
	Report containing the final design and technical specifications of the interaction platforms. 
	\vspace{0.2cm}
	\\ \midrule

	Data Processing Software  & 
	Final data processing algorithms based on applications to process acquired satellite data. 
	\vspace{0.2cm}
	\\ \midrule

	Validation & 
	Report that gathers the tests and validations with the obtained results of all the payload sensors, the modular system and the interaction platform, as well as the full system performing. 
	\vspace{0.2cm}
	\\ \midrule
		
	Final Report & 
	Final document that includes all the development done through the execution of the project. 
	\vspace{0.2cm}

	\\ \bottomrule[2pt]
	
	\caption{Project Deliverables}
	\label{PDel}

\end{longtable}