\section{Project Acceptance Criteria}

The acceptance criteria establish the requirements that must be met for the client to accept the project. These criteria are quantifiable, demonstrable and verifiable in such a way as to demonstrate that the project has been carried out properly, that is why, if these criteria are not met, a deliverable of the project cannot be considered valid.

\begin{longtable}[H]{lp{10.2cm}}
	
	\toprule[2pt]
	
	\textbf{Item} & \textbf{Description} \\
	
	\midrule[1.5pt] 
	\endhead
	
	\textbf{Management} & \vspace{0.2cm} \\

	\midrule[1.5pt]
	
	Quality & The content of the project documentation must be clear, complete and understandable. Furthermore, it must be well structured, dividing the information into approach, development, and conclusions.\vspace{0.2cm}
	\newline
	All the documentation included in the project must first pass through an inspection of the quality department.\vspace{0.2cm} \\

	\midrule	
	
	Schedule & The organization must be well structured and the deadlines must be met in a timely manner so that the development of the product is appropriate.\vspace{0.2cm} \\
	
	\midrule
	
	Clarity & The tasks of the project must be well defined, both individually and as a group, in such a way that each of the contributors knows their duty and the duty of their team.\vspace{0.2cm} \\
	
	\midrule
	
	Viability & The project must be viable economically and technically so that its realization is possible.\vspace{0.2cm}
	\newline
	The different parts of the project must be submitted at the individual level to a study that checks if it is possible to do them and, if not, search for an alternative.\vspace{0.2cm}
	\newline
	The budget of the project must comply with the financial requirements of the European Union. Hence, a balance is to be made to ensure that the allowed limit is not exceeded.\vspace{0.2cm}\\
	
	\midrule
	
	Collaboration & It is interesting to obtain a better result to collaborate with legal entities from different countries, like universities and research groups. Moreover, some collaborations with SMEs should be tried, so that they can benefit and grow in the market.\vspace{0.2cm} \\
	
	\midrule
	
	Transparency & In case information about the project is required by part of official organizations of the European Union or by the different stakeholders that participate in it, transparency has to be considered when sharing information.\vspace{0.2cm} \\
	
	\midrule
	
	Legal requirements & The applications and products of this project must have if required, the certification and approval of the different legislative and ethical frameworks.\vspace{0.2cm} \\
			
	\midrule[1.5pt]
	
	\textbf{Technical} & \vspace{0.2cm} \\
	
	\midrule[1.5pt]
	
	Research and innovation & The project must be ambitious and use all the available resources to obtain the best result. In this way, it must include the most appropriate technology that there is so far and, if it is in the development phase, add a section of research.\vspace{0.2cm} \\
	\midrule			
		
	Test and validations & The evaluation and validation tests must be carried out periodically and be registered in the project documentation, in such a way that there is a record of the different versions of the application throughout the development.\vspace{0.2cm}
	\newline
	The information of these tests must be presented clearly and refer to the regulations concerned, in addition, to be verifiable.\vspace{0.2cm}
	\newline
	The results of these tests should be used to analyze the service level of the application and improve on later versions.\vspace{0.2cm} \\
	
	\midrule
	
	Technical documents & The application must have a user manual both internally and externally and attach the necessary information for its development.\vspace{0.2cm}
	\newline
	The performance of the final product must be reflected in a data sheet. It must also be included in the documentation the datasheet of the different components that are part of the application.\vspace{0.2cm} \\
	
	\midrule[1.5pt]
	
	\textbf{Performance} & \vspace{0.2cm} \\
	
	\midrule[1.5pt]
	
	Size & The total volume of the module must not exceed the space allocated to it. Considering that the system can be integrated into several satellites, this volume should not exceed 500 $dm^{3}$.\vspace{0.2cm} \\

	\midrule	
	Weight & The system must be light enough to allow it to be put into orbit with ease and not affect the subsequent operation of the satellite in which it will remain during the data collection. In this way and making an estimation of the density of the materials and the maximum volume of the system, a limit weight of 950 kg is defined, which must not be exceeded for the system to be accepted as valid.\vspace{0.2cm} \\
	

	\midrule	
	
	Power consumption & Modular system maximum power consumption must be lower than the 50\% available onboard.\vspace{0.2cm} \\
	
	\midrule
	
	Accuracy & The accuracy of the equipment should allow the samples to be taken in a way that provides discretized information in the space. Due to the homogeneity of the climatology, the precision for this will be of 1 $m^{3}$, whereas in the 3D mapping in which there can be more considerable variations, it will be of 25 $cm^{3}$.\vspace{0.2cm} \\

	\midrule	
	Back-up & Back-up system prepared to handle up to two major failures in the system. A major failure can be defined as the loss of a sensor module of the same type.\vspace{0.2cm} \\

	\midrule	
	Transmission velocity & Transmission velocity between modular system and the main satellite communication (SATCOM) system should be able to handle at least 250 Mbit/s of data rate.\vspace{0.2cm} \\

	\midrule	
	Processing time & The time that elapses since the information is captured by the sensors until it is processed and prepared to send to the ground station to be analyzed should not exceed 10 seconds.\vspace{0.2cm} \\

	\midrule	
	Latency & The latency, since the information is prepared in the system located on the satellite to be sent to the ground station until this station is finally processed, should not exceed 300 seconds. The information collected by the system must be available via the Internet in less than 8 minutes. This means that after the processing of information it must be sent in less than 3 minutes for the system to be considered valid.\vspace{0.2cm} \\

	\midrule[1.5pt]	
	
	
	\textbf{Social} & \vspace{0.2cm} \\
	
	\midrule[1.5pt]
		
	Sustainability & The product must be sustainable using renewable energy as much as possible and avoiding excessively polluting emissions. The materials used in the project must be reliable and guarantee the agreed useful life of the product.\vspace{0.2cm} \\
	
	\midrule		
	
	Social contribution & The product must be able to solve a current problem and improve the quality of life of people using technology.\vspace{0.2cm} \\
	
	\midrule
	
	Gender equality & The selection process must be fair, based on the knowledge and personal competencies of each person regardless of gender or condition.\vspace{0.2cm} \\

	
	\bottomrule[2pt]
	
	\caption{Acceptance criteria}
\end{longtable}