\section{Project Exclusions}

There are some facts that are out of the scope of the project which, generally, are designated as exclusions. Hence, in this section, the exclusions of the project are determined and defined. 

\begin{longtable}[H]{lp{11cm}}
	
	\toprule[2pt]
	
	\textbf{Item} & \textbf{Description} \\
	
	\midrule[1.5pt] 
	\endhead
	
	Satellites design & It is out of the scope of this project to design a new satellite that will use the sensors as payload.\vspace{0.2cm} \\
	
	\midrule
	
	Launching  & The objective of the project do not include either the design of the launch system of the satellites nor the costs and scheduling of launching the satellite using the sensors designed.\vspace{0.2cm} \\
	
	\midrule
	
	Deployment & No deployment mechanism nor the strategy of the satellites that integrate these new technologies are going to be developed.\vspace{0.2cm} \\
	
	\midrule
	
	Satellite monitoring & The satellite monitoring system that permits to scan different surfaces and regions of the earth is not included in this project scope.\vspace{0.2cm} \\
	
	\midrule
	
	Data transfer & Neither communication between satellites nor between the satellite and the ground station are part of this project.\vspace{0.2cm} \\
	
	\midrule
		
	Final production & The project will only focus on the development of prototype models in order to test the new technologies implemented. Hence, commercial production of these ones will not be carried out.\vspace{0.2cm} \\
	\bottomrule[2pt]
	
	\caption{Project Exclusions}
\end{longtable}